UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-14 main.tex
:pencil: Update scattering principles

	\begin{subsection}{BackCom/SR: Backscatter Modulation}
		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as backscatter information sources.
		% Backscatter information sources of \gls{bc} and \gls{sr} encode self message by \emph{random reflection states variation.}
		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude scattering ratio at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
		% TODO by switching between reflection states, backscatter modulation introduces uncertainty.

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		% \gls{ris} involves numerous
		\gls{ris} involves either a planar scattering antenna array or a metasurface of numerous metamaterial units.
		% Reflecting elements of \gls{ris} assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{subsection}{UniScatter: Bridge and Generalization}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
			}
			\caption{
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			}
			\label{fi:uniscatter}
		\end{figure}
		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
		% As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.

>>>>

	\begin{subsection}{BackCom/SR: Backscatter Modulation}
		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as passive information sources.
		By \emph{frequently switching} between the available states, each backscatter node encodes self message over scattered signal and introduces backscatter uncertainty at the receiver.
		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude scattering ratio at the direction of interest.
	\end{subsection}

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		% \gls{ris} involves numerous
		\gls{ris} typically involves a planar antenna array or metasurface of numerous metamaterial units as a passive channel reconfigurator.
		% By \emph{adaptively deciding} the reflection pattern, each reflecting element alters the phase of reflected signal for constructive/destructive superposition at the receiver.
		By \emph{adaptively choosing} the reflection pattern, each reflecting element alters the phase of scattered signal for constructive/destructive superposition at the receiver.
		% Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
		% Reflecting elements of \gls{ris} assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{subsection}{UniScatter: Bridge and Generalization}
		% TODO compare BC, SR and IRS
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
			}
			\caption{
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			}
			\label{fi:uniscatter}
		\end{figure}
		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
		% As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.
